Logistic Regression, MLP and Random Forest with Sklearn and Feed Forward Neural Net with PyTorch on Baxter Dataset

### 2018-08-08 sklearn_pyTorch_baxter.Rmd
export as pdf

---
title: "Logistic Regression, MLP and Random Forest with Sklearn and Feed Forward Neural Net with PyTorch on Baxter Dataset"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE)
library(reticulate)
use_python("/Library/Frameworks/Python.framework/Versions/3.6/bin/python3", required = TRUE)
py_config()

@@

#### Predict using the Random Forest model on the test set

```{python,comment='[Output]', cache=FALSE, message=FALSE, warning=FALSE, engine.path = '/Library/Frameworks/Python.framework/Versions/3.6/bin/python3'}
y_pred = rfc.predict(x_test)
print("Performance Accuracy on the Testing data:", round(rfc.score(x_test, y_test) *100))
print("Number of correct classifiers:", round(accuracy_score(y_test, y_pred, normalize=False)))
```

#### Now let's define a 1 hidden layer(n=100) Feed Forward Neural Net
```{python,comment='[Output]', cache=FALSE, message=FALSE, warning=FALSE, engine.path = '/Library/Frameworks/Python.framework/Versions/3.6/bin/python3'}

@@

## ROC plot for training
pyTorch_plot = plt.figure()
tprs = []
aucs = []
mean_fpr = np.linspace(0, 1, 100)
for epoch in range(num_epochs):
    x_train, y_train = shuffle(x_train, y_train)
    # Mini batch learning
    for i in range(batch_no):
        start = i * batch_size
        end = start + batch_size
        x_var = Variable(torch.FloatTensor(x_train.values[start:end]))
        y_var = Variable(torch.LongTensor(y_train.values[start:end]))
        # Forward + Backward + Optimize
        ypred_var = net(x_var)
        loss =criterion(ypred_var, y_var)
        correct_num = 0
        ## The outputs of the model (ypred_var) are energies for the 10 classes. Higher the energy for a class, the more the network thinks that the image is of the particular class. So, let’s get the index of the highest energy:
        values, labels = torch.max(ypred_var, 1)
        correct_num = np.sum(labels.data.numpy() == y_var.numpy())
        fpr, tpr, thresholds = roc_curve(y_var.numpy(), labels.data.numpy())
        tprs.append(interp(mean_fpr, fpr, tpr))
        tprs[-1][0] = 0.0
        roc_auc = auc(fpr, tpr)
        aucs.append(roc_auc)
        #plt.plot(fpr, tpr, lw=1, alpha=0.3, label='ROC fold %d (AUC = %0.2f)' % (epoch, roc_auc))
        optimizer.zero_grad()
        loss.backward()
        optimizer.step()
        print('Epoch [%d], Loss:%.4f, Accuracy:%.4f' % (epoch, loss.data[0], correct_num/len(labels)))

>>>>

---
title: "Logistic Regression, MLP and Random Forest with Sklearn and Feed Forward Neural Net with PyTorch on Baxter Dataset"
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
fontsize: 10pt
output: pdf_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(reticulate)
use_python("/Library/Frameworks/Python.framework/Versions/3.6/bin/python3", required = TRUE)
py_config()

@@

#### Predict using the Random Forest model on the test set
```{python,comment='[Output]', cache=FALSE, message=FALSE, warning=FALSE, engine.path = '/Library/Frameworks/Python.framework/Versions/3.6/bin/python3'}
y_pred = rfc.predict(x_test)
print("Performance Accuracy on the Testing data:", round(rfc.score(x_test, y_test) *100))
print("Number of correct classifiers:", round(accuracy_score(y_test, y_pred, normalize=False)))
```
#### Now let's define a 1 hidden layer(n=100) Feed Forward Neural Net
```{python,comment='[Output]', cache=FALSE, message=FALSE, warning=FALSE, engine.path = '/Library/Frameworks/Python.framework/Versions/3.6/bin/python3'}

@@

## ROC plot for training
pyTorch_plot = plt.figure()
tprs = []
aucs = []
mean_fpr = np.linspace(0, 1, 100)
for epoch in range(num_epochs):
    x_train, y_train = shuffle(x_train, y_train)
    # Mini batch learning
    for i in range(batch_no):
        start = i * batch_size
        end = start + batch_size
        x_var = Variable(torch.FloatTensor(x_train.values[start:end]))
        y_var = Variable(torch.LongTensor(y_train.values[start:end]))
        # Forward + Backward + Optimize
        ypred_var = net(x_var)
        loss =criterion(ypred_var, y_var)
        correct_num = 0
        ## The outputs of the model (ypred_var) are energies for the 10 classes. 
        #Higher the energy for a class, the more the network thinks that the image is of the         #particular class. So, let’s get the index of the highest energy:
        values, labels = torch.max(ypred_var, 1)
        correct_num = np.sum(labels.data.numpy() == y_var.numpy())
        fpr, tpr, thresholds = roc_curve(y_var.numpy(), labels.data.numpy())
        tprs.append(interp(mean_fpr, fpr, tpr))
        tprs[-1][0] = 0.0
        roc_auc = auc(fpr, tpr)
        aucs.append(roc_auc)
        #plt.plot(fpr, tpr, lw=1, alpha=0.3, label='ROC fold %d (AUC = %0.2f)' % (epoch, roc_auc))
        optimizer.zero_grad()
        loss.backward()
        optimizer.step()
        print('Epoch [%d], Loss:%.4f, Accuracy:%.4f' % (epoch, loss.data[0], correct_num/len(labels)))
